### 2019-11-12 cvpr_submission/introduction.tex
Reverted modifications to the Related Work section.
Corrected some typos.

In computer vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
That such transfer improves performance is appealing, knowing that both the domain (e.g. realistic images vs. medical ones or images with cars) and the task (e.g. image classification vs. VQA or image segmentation) can change significantly. This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.

@@

The contributions of this paper are as follows.
We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
\begin{itemize}
	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}. We analyze how training exclusively on one task family helps with mastering the others, with one notable difference: we transfer and fine-tune the whole model (not only the encoder or input layer).
	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e. a higher number of distractor objects present in each frame).
\end{itemize}
Surprisingly, our model with only small fine-tuning, managed to the master Hard variant and achieved higher accuracy than the model trained explicitly on Hard variant from the scratch.

@@

\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR | 4. Ablation study ("all-but-one") in CLEVR and the limitations of transfer learning (e.g. the labels domains should be aligned)}.

>>>>

In Computer Vision, it is now standard practice to pre-train an image encoder (such as VGG~\cite{simonyan2014very} or ResNet~\cite{he2016deep}) on large-scale datasets (such as ImageNet~\cite{deng2009imagenet}), and reuse the weights in unrelated domains and tasks, such as Visual Question Answering (VQA) in a medical domain~\cite{kornuta2019leveraging} or pixel-wise image segmentation of cars~\cite{iglovikov2018ternausnet}.
That such transfer improves performance is appealing, knowing that both the domain (e.g. realistic images vs. medical or cars ones) and the task (e.g. image classification vs. VQA or image segmentation) can change significantly. This type of transfer learning is qualified as \emph{inductive}, according to the taxonomy from~\cite{pan2009survey}.

@@

The contributions of this paper are as follows.
We propose a new model, called SAMNet (Selective Attention Memory Network), which achieves state-of-the-art results on two datasets for Visual Reasoning, namely CLEVR~\cite{johnson2017clevr}, a diagnostic dataset for Image QA, and COG~\cite{yang2018dataset}, a Video QA reasoning dataset.
We show the impact of the different tasks when transferring the whole pretrained model in three main setups.
\begin{itemize}
	\item We first focus on transfer learning within the Image QA domain and perform experiments similar to Taskonomy~\cite{zamir2018taskonomy}. We analyze how training exclusively on one task family helps with mastering the others, with one notable difference: we transfer and fine-tune the whole model (not only the encoder or input layer).
	\item Next, we show complementary results in a multi-task learning setup, when the model is trained on all-but-one task and then tested on this task (with and without finetuning).
	\item Finally, we present a set of experiments aimed at analyzing of the impact of transfer learning in Video QA, when domain changes drastically and the model is forced to handle longer videos with higher complexity (i.e. a higher number of distractor objects present in each frame).
\end{itemize}
Surprisingly, our model, with only small fine-tuning, managed to master the Hard variant of the COG dataset and achieved higher accuracy than the model trained solely on the Hard variant.

@@

\vm{I think the contributions should be: 1. A new model with SotA results on COG |  2. transfer  / multitask learning  in COG | 3.  transfer  / multitask learning  in CLEVR}.

### 2019-11-12 cvpr_submission/related_work.tex
Corrected some typos.

@@

Another research focus area has been multimodal fusion and
attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
features \cite{zhou2015simple, antol2015}.  Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard, kim2016hadamard} .  Attention  research in VQA have demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}.   Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}.   Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach.  The follow-on model by the same authors  \cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features.  Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video question answering, aside from spatial queries, also focuses on questions that require temporal reasoning .  Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text to leverage temporal attention to attend to essential frames in a video selectively.   These approaches might be sufficient for action-recognition types of tasks but fall short when spatio-temporal reasoning is required.  Learning long-term dependencies is also another challenge that LSTMs may struggle with.  Yin et al. 2019 \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input.  Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \textit{access to all frames}.  Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

>>>>

%\section{Related work -- import}
%Integration of vision and language in deep neural network models allows the system to learn joint representations of objects, concepts, and relations.  Potentially, this approach can lead us towards Harnad's \textit{symbol grounding problem}~\cite{harnad2003symbol} but we are quite far from achieving the full capabilities of visually grounded language learning.

%Recently, there is a growing interest in neuro-symbolic approaches, which can combine the power of representation learning and symbolic logic that is interpretable \cite{mao2019neurosymbolic}. These approaches focus on \textit{symbol manipulation} rather than learning \textit{grounded symbols}.  Furthermore, symbolic priors (e.g., domain knowledge) and integration of logic depend on hand-crafted modules.  In the near term, this direction is certainly promising and can address some of the shortcomings of machine learning (i.e., the lack of explainability)\cite{vedantam2019probabilistic}.  However, in the long run, the desire is to learn grounded representations, which may lead to the emergence of symbols \cite{taniguchi2018symbol}.

%Starting with Image Question Answering~\cite{malinowski2014multi,antol2015} and Image Captioning~\cite{karpathy2015deep}, a variety of tasks that integrate vision and language have appeared in the past several years~\cite{mogadala2019trends}. 
%Those directions include e.g., Video QA~\cite{MovieQA} and Video Action Recognition~\cite{monfort2019moments}, that provide an additional challenge of understanding \emph{temporal} aspects, and Video Reasoning~\cite{song2018explore,yang2018dataset}, that tackles both spatial (comparison of object attributes, counting and other relational question) and temporal aspects and relations (e.g. object disappearance).
%To deal with the temporal aspect most studies typically cut the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by aggregation over clips to form a single video representation.
%Still, when reasoning and producing the answer, the system in fact has \textit{access to all frames}. 
%Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history.
%However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.

%As evident from human cognition, attention and memory are the key competencies required to solve these problems, and unsurprisingly, the AI research is rapidly growing in these areas.
%The ability to deal with temporal casuality can pose a challenge for also in pure natural language processing (NLP) settings, e.g. in question answering (QA) and dialog applications.  
%Current NLP solutions, in many problem settings, work around this challenge by processing the entire text input and reason over it multiple times using attention \cite{vaswani2017attention} or other mechanisms.
%For example, typical solutions to the bAbI reasoning task, such as Memory Networks \cite{weston2014memory}, involve processing all the supporting facts at once and keeping them in memory all the time while searching for the answer.

@@

Another research focus area has been multimodal fusion and
attention for VQA. For multimodal fusion, earlier methods used concatenation or element-wise multiplication between multimodal
features \cite{zhou2015simple, antol2015}. Others proposed more sophisticated methods such as different approximated bilinear pooling methods to effectively integrate the multimodal features with second-order feature interactions \cite{fukui2016multimodal, kim2016hadamard}. Attention  research in VQA has demonstrated that learning question-guided visual attention on image regions is the most promising approach \cite{yang2016stacked, chen2015abc, ilievski2016focused}. Compositional reasoning tasks such as the CLEVR dataset, also benefit from multi-hop attention and reasoning methods \cite{hudson2018compositional, song2018explore}. Visualization of attention steps also provide interpretability, which is an increasingly important aspect. The MAC model \cite{hudson2018compositional} is a great example of such an approach. The follow-on model by the same authors~\cite{hudson2019learning}, called Neural State Machine (NSM) takes a slightly different approach and reason over graph structures rather than directly over spatial maps of visual features. Representing objects in a scene and their relationship as a graph is an obvious choice, which is another growing research direction \cite{haurilet2019s, teney2017graph, kim2018dynamic}.

Video Question Answering, aside from spatial queries, also focuses on questions that require \emph{temporal} reasoning. Early works \cite{mun2017marioqa, xu2017video, yu2017end} used LSTMs to encode video frames and text queries to leverage temporal attention to selectively attend to essential frames in a video. These approaches might be sufficient for action-recognition type of tasks but fall short when spatio-temporal reasoning is required. Learning long-term dependencies is also another challenge that LSTMs may struggle with. Yin et al. \cite{yin2019memory} recently proposed a memory-augmented neural network (MANN) architecture for video QA which leverages the external memory for storing and retrieving useful information in questions and videos and modeling the long-term visual-textual dependence.
Our work is mostly related to the MAC and MANN type models. An important distinction of our approach is the frame-by-frame processing of the video input. Prior studies typically divide the whole video into clips; e.g., in~\cite{song2018explore} the model extracts visual features from each frame and aggregates features first into clips, followed by an aggregation over clips to form a single video representation.
Nevertheless, when reasoning and producing the answer, the system has \emph{access to all frames}. Similarly, in Visual Dialog~\cite{das2017visual} the system memorizes the whole dialog history. However, in real-time dialog or video monitoring, it is not always possible to keep the entire history of conversation nor all frames from the beginning of the recording.
